### 2016-05-19 text/ms.Rmd
Integrate comments from Jess and Kristin

\noindent \textbf{Abstract:}
Fishery managers must often reconcile conflicting estimates of population status and trend. Superensemble models, commonly used in climate and weather forecasting, may provide an effective solution. This approach uses predictions from multiple models as covariates in an additional "superensemble" model fitted to known data. We evaluated the potential for ensemble averages and superensemble models ("ensemble methods") to improve estimates of population status and trend for fisheries. We fit four widely applicable data-limited models that estimate stock biomass relative to the equilibrium biomass at maximum sustainable yield ($B/B_\mathrm{MSY}$). We combined estimates of recent fishery status and trends in $B/B_\mathrm{MSY}$ with four ensemble methods: an ensemble average and three superensembles (a linear model, random forest, and boosted regression tree). We trained our superensembles on a simulated dataset of 5760 stocks and tested them with cross-validation and against a global database of `r ram_stocks_n` stock assessments. Ensemble methods substantially improved estimates of population status and trend. Random forest and boosted regression trees performed the best at estimating population status: accuracy improved `r mean_sim$mach_vs_ind_mare_fold`%, rank-order correlation between predicted and true status improved from `r mean_sim$ind_corr_range` to `r mean_sim$mach_corr_range`, and bias (median proportional error) declined from `r mean_sim$ind_mre_range` to `r mean_sim$mach_mre_range`. We found similar improvements when predicting trend and when applying the simulation-trained superensembles to catch data for global fish stocks. Ensemble methods can improve estimates of status and trends; however, they must be tested, formed from a diverse set of accurate models, and built on a dataset representative of the populations to which they are applied.

@@

Status and trend are two of the most fundamental values to quantify in the
management of ecological populations [e.g. @hutchings2010; @iucn2015]. However,
managers are often faced with reconciling multiple uncertain and potentially
conflicting estimates of status and trend [e.g. @brodziak2010; @branch2011;
@deroba2015]. For example, one model may suggest a population is at risk and
declining in abundance while others may suggest it is not at risk and stable.

One solution is to take the average or weighted average of several model
predictions, i.e. an ensemble. Such ensembles are typically more accurate and
less biased than individual model estimates and can integrate uncertainty in
model structure, initial conditions, and parameter estimation
[@dietterich2000; @araujo2007]. Ensembles are superior to individual models
in at least three ways: (1) statistically by averaging across models and
therefore being less likely to pick the "wrong" model, (2) computationally by
reducing the risk of getting stuck in a local optima, and (3)
representationally by expanding the range of hypotheses explored
[@dietterich2000]. This approach forms the basis of many machine learning
methods [e.g. @dietterich2000], has helped reconcile climate forecasts from
dozens of models [e.g. @murphy2004; @tebaldi2007; @ipcc2013], and even
improved early warning signs of malaria outbreaks [@thomson2006]. In ecology,
ensemble methods are sometimes used to improve species distribution modelling
[e.g. @araujo2007; @breiner2015] and indeed have been used to combine
estimates of population status and trend [e.g. @brodziak2010].

@@

We can exploit these characteristics by using the predictions from a group of
models as inputs into a separate statistical model. This technique, sometimes
called superensemble modelling [@krishnamurti1999], is common in climate and
weather forecasting [e.g. @yun2005; @mote2015]. The superensemble is fit to a
training dataset where outcomes are well known and then used to predict on a
dataset of interest. For example, @krishnamurti1999
combined predictions of wind and precipitation in Asian monsoons via a
superensemble regression fit to observed data. Their superensemble was
considerably more accurate than any individual prediction or weighted average
of predictions.

In fisheries science, the commonly used operational models for determining
status and trend of exploited fish populations are stock assessments, i.e.,
population models coupled to an observation model that incorporate all
appropriate data (e.g. catches, size and age distributions, surveys, and
tagging information) to quantify values such as the biomass of a stock that
can produce maximum sustainable yield ($B_\mathrm{MSY}$) [@hilborn1992].
However, the broad range of data required to conduct these stock assessments
are not available for the majority of fish populations, including those of
conservation concern and of economic interest to fisheries [@fao2014].
Therefore, a number of models have been proposed to assess $B/B_\mathrm{MSY}$
based on the limited data available for the majority of fish stocks: (1) a time
series of the total biomass of catch and (2) a basic understanding of
population productivity [e.g. @vasconcellos2005; @martell2013]. Recently,
@rosenberg2014 investigated the performance of four data-limited models through
a large-scale simulation experiment. Three of these models were based on
Schaefer (logistic) biomass dynamics and one was an empirical model fitted to
more data-rich stock-assessment output. The four models frequently disagreed
about population status (e.g. Fig. \ref{motivate}), no one model had strong
performance across all fish stocks, and some models performed better than
others depending on circumstances.

@@

To test the ability of superensembles to improve estimates of status and trend in data-limited fish stocks, we first fit four individual assessment models to a large simulated dataset of fish stocks. We then built and tested the performance of superensembles using cross-validation of the simulated dataset. Finally, we tested superensembles built with the entire simulated dataset against a database of global fish sticks. We describe these steps in detail below and illustrate the general approach both with illustrations and pseudocode in Fig. 2.

@@

* *CMSY* (catch-MSY) implements a stock-reduction analysis with Schaefer
  biomass dynamics [@martell2013]. It requires a prior distribution for $r$
  and a prior on the relative proportion of biomass at the end of the time
  series compared to unfished biomass (depletion), which is derived from the
  percentage of maximum catch at the end of the time series. The version of
  the model used in @rosenberg2014 was modified from @martell2013 to generate
  biomass trends from all viable $r$-$K$ pairs and produce an estimate of
  $B/B_\mathrm{MSY}$ from the median trend.

@@

We first developed and tested ensemble methods on a fully factorial simulated
dataset of fisheries [@rosenberg2014] with known status. These simulated data
included the following scenarios: three fish life histories: small pelagic,
demersal, and large pelagic; three levels of initial biomass depletion
compared to carrying capacity: biomass at 100%, 70%, and 40% of carrying
capacity; and four exploitation settings: (1) a constant exploitation rate,
(2) an exploitation rate coupled with biomass to mimic an open-access
single-species fishery, (3) a scenario where exploitation rate increased
continuously, and (4) a "roller-coaster" scenario where the exploitation
rate increased and then decreased. Process noise (recruitment variability;
i.e. unexplained variability in population dynamics) was introduced to the
models at two magnitudes in log space, $N(0, 0.2^2)$ and $N(0, 0.6^2)$,
and was either uncorrelated through time or had first-order autoregressive
correlation of $0.6$. The simulation also included a scenario with $N(0,
0.2^2)$ measurement error around log(catch) and one scenario without
measurement error. @rosenberg2014 ran ten iterations for each combination
of factors adding stochastic draws of recruitment and catch-recording
variability each time to generate a total of 5760 stocks. The simulation
models were built in the `FLR` packages [@kell2007,
<http://flr-project.org>] for the statistical software R. Code to
generate the simulations is available at
<https://github.com/iagomosqueira/stockStatusFAO>.

@@

The individual models we seek to combine with superensembles provide time series
of stock status ($B/B_\mathrm{MSY}$). Therefore, we can use superensembles to
estimate any property of these time series. Here, we focus on two properties:
the mean and slope of $B/B_\mathrm{MSY}$ in the last five years. Together, these
quantities address the recent state and trend of stock status, which are both of
management and conservation interest [e.g. @hutchings2010; @iucn2015]. To avoid
undue influence of the time series end points on the calculated slope, we
measured the slope as the Theil-Sen estimator of median slope [@theil1950].

@@

TODO add short description of spectral densities

@@

Once the superensemble models are built, we can apply them to new stocks to
estimate their status (Fig. \ref{didactic}b). To do this we applied the
individual models to our stocks of interest and then applied these data to our
already built superensemble models. In this paper we applied the superensemble
models to subsets of the simulated data as a cross-validation test and to the
RAM Legacy Stock Assessment database to test on real stocks.

We used repeated three-fold cross validation to test predictive performance: we
randomly divided the dataset into three sets, built superensemble models on
two-thirds of the data, and evaluated predictive performance on the remaining
third. We repeated this across each of the three splits and then repeated the
whole procedure 50 times to account for bias that may result from any one set
of validation splits. In the simulated dataset, there were 10 replicates of
each unique combination of simulation parameters that differed only in
stochastic variability. Since the dynamics of these populations were often
similar, we grouped these stocks in the cross-validation process into either
the training or testing split.

@@

Predictive performance can be evaluated with metrics that represent a variety
of modelling goals. For continuous response variables such as the mean and
slope of population status, performance metrics often measure some form of
bias, precision, accuracy (a combination of bias and precision), or the ability
to correctly rank or correlate across populations [e.g. @walther2005]. Here, we
measure proportional error, defined as $(\hat{\theta} - \theta)/\abs{\theta}$,
where $\hat{\theta}$ and $\theta$ represent estimated and "true" (or
stock-assessed) mean or slope of $B/B_\mathrm{MSY}$. We calculated median
proportional error to measure bias, median absolute proportional error to
measure accuracy, and Spearman's rank-order correlation between predicted and
"true" values to measure the ability to correctly rank populations. When
testing with the RAM Legacy Stock Assessment database, we treated the
estimates from these data-rich stock assessments as known without error. Thus,
any error in the stock-assessment estimates of the mean or slope of
$B/B_\mathrm{MSY}$ also contributes to our estimates of prediction error for
each of the four data-limited models and the ensembles. Code to reproduce our
analysis is available at <https://github.com/datalimited/ensembles> (*Private while in
review*).

@@

Applied to the simulated dataset of known stock status, the individual models
had variable success at recovering the mean (status) and slope (trend) of
$B/B_\mathrm{MSY}$ in the last five years. All models exhibited a high degree of
scatter around the one-to-one line of perfect status prediction (Fig.
\ref{hexagon}). In contrast to the known unimodal distribution of status, CMSY
exhibited bimodal predictions (Fig. \ref{hexagon}a), but had the best rank-order
correlation and accuracy scores (Fig. \ref{performance}a). COM-SIR and SSCOM
both correctly identified a number of stocks with low status, but frequently
predicted a high status when status was in fact low (Fig. \ref{hexagon}b, c).
mPRM had relatively poor ability to predict status for the simulated dataset
(Fig. \ref{hexagon}d). There was generally little correlation between true and
predicted recent trend in status for any of the individual models (rank-order
correlation = `r range_slope_corr_non_sscom`) with the exception of SSCOM
(correlation = `r slope_corr_sscom`; Figs \ref{scatter-sim-slope}a--d).

@@

Ensemble methods provide a useful approach to situations where environmental
resource management decisions must be made on the basis of multiple,
potentially contrasting estimates of status. Compared to individual models of
fish population status, ensemble methods were consistently the best or among
the best across three performance dimensions (accuracy, bias, and rank-order
correlation), two response variables (status and trend), two datasets
(simulated and global fisheries), and multiple ensemble methods (from a simple
average to machine learning superensembles). Our results suggest choosing a
superensemble model that allows for non-linear relationships, such as
machine learning methods. These methods provide added insight into individual
model behavior and generally performed the best; however, even a simple average
of predictions across multiple models may provide a more useful metric than a single model in many cases.

Certain conditions will make some ensemble models more effective than others.
First, ensembles will be most effective when they are comprised of diverse
individual models that choose different structural model forms, explore
contrasting but plausible ranges of parameter values, and make uncorrelated
errors [@ali1996; @dietterich2000; @tebaldi2007]. We would expect such models
to perform well in different conditions and an ensemble model can
exploit the best predictive performance of each. Second,
ensemble models will be most effective when they are not overfit to the
training dataset. Cross-validation testing [@caruana2004; @hastie2009] and
methods that are robust to overfitting such as random forests [@breiman2001],
may help avoid overfitting ensemble models. We note that our simplest ensemble
model, an average of individual model predictions, performed approximately as
well as complex machine learning models when we trained our superensembles on
the simulation dataset and tested them on a separate "real" dataset (i.e. the
RAM Legacy Stock Assessment database, Fig. \ref{performance}b). Third, ensemble
models will be most effective when they are trained on data that are
representative of the dataset of interest [@knutti2009; @weigel2010].
Cross-validation within a training dataset will provide an optimistically
biased impression of predictive performance if the training dataset
fundamentally differs from the dataset of interest [@hastie2009].

Multi-model inference in the form of coefficient averaging weighted by
information theoretics such as the Akaike Information Criterion (AIC) is
a common analytical approach in fisheries and ecology [e.g. @burnham2002; @johnson2004;
@grueber2011]. The ensemble methods described in this paper share similarities
with coefficient averaging but differ in other important ways. Ensemble methods
and coefficient averaging share the long-held notion that multiple working
hypotheses can contribute useful information for inference [@chamberlin1890].
A fundamental difference is that coefficient averaging focuses on averaging
*coefficients* whereas ensembles instead average *predictions*. Thus, ensembles
provide a general purpose tool: they do not require information theoretics
and they can combine different types of models (e.g. parametric and
non-parametric models or frequentist and Bayesian predictions). Furthermore,
superensembles extend these benefits by allowing model predictions to be
combined via non-linear functions that are tuned to known data.

A strength of superensembles is that they can be tailored to predict specific
response variables. For example, we built separate superensemble models of mean
$B/B_\mathrm{MSY}$ and the slope of $B/B_\mathrm{MSY}$. The same set of model
weights or non-linear relationships need not hold across different response
variables. For instance, SSCOM contributed little to the GBM superensemble
estimate of status at higher levels of predicted $B/B_\mathrm{MSY}$ (Fig.
\ref{partial-sim}), but contributed strongly to estimates of trend (Fig.
\ref{partial-sim-slope}). Formally, fitting superensemble models to specific
quantities of interest provides an additional calibration step [@rykiel1996].
Individual models are typically calibrated (i.e. parameters are estimated) based
on a single response variable; however, this model might then provide a biased
or inaccurate estimate of other quantities of interest. Ensemble methods provide
a final calibration step to a quantity of interest. This ensemble calibration
could further include a loss function tailored to the goals of the model, say
placing greater weight on accuracy at lower rather than higher status levels.
Conversely, because superensembles are tailored to a specific response and loss
function, superensembles force a modeller to choose an operational purpose for
their model up front [*sensu* @dickey-collas2014].

@@

Combining predictions from multiple models via superensemble methods is
broadly useful in other subfields of fisheries science and ecology in general.
Predictions about extinction risk are widely used at the national (e.g. the US Endangered
Species Act and the Canadian Species at Risk Act) and international [e.g. the
IUCN Red List, @iucn2015] levels. These risk assessments generally involve
fitting regression models to outcomes for individual species along with
predictors of extinction risk [e.g. @anderson2011a; @pinsky2011], or fitting population-dynamic models to data for individual species [e.g. @dfo2010]. Both types of
models are prone to error caused by model-misspecification and therefore results
are sensitive to decisions about model structure [@brooks2015]. Although there
are options to account for potential model-misspecification in determination of
species risk [e.g. coefficient averaging, @burnham2002; generalized modeling,
@yeakel2011; or semi-parametric methods, @thorson2014], ensemble methods are
a relatively simple way to combine predictions in a transparent manner. Beyond
estimates of status and trend, ensemble methods could be used, for example, to
increase the robustness of spatial predictions when designing networks of
protected areas [@rassweiler2014] or to forecast potential spatial shifts in
species distribution given climate impacts [@harsch2014].

>>>>

\noindent \textbf{Abstract:} Fishery managers must often reconcile conflicting
estimates of population status and trend. Superensemble models, commonly used in
climate and weather forecasting, may provide an effective solution. This
approach uses predictions from multiple models as covariates in an additional
"superensemble" model fitted to known data. We evaluated the potential for
ensemble averages and superensemble models ("ensemble methods") to improve
estimates of population status and trend for fisheries. We fit four widely
applicable data-limited models that estimate stock biomass relative to the
equilibrium biomass at maximum sustainable yield ($B/B_\mathrm{MSY}$). We
combined these estimates of recent fishery status and trends in $B/B_\mathrm{MSY}$
with four ensemble methods: an ensemble average and three superensembles (a
linear model, random forest, and boosted regression tree).  We trained our
superensembles on a simulated dataset of 5760 stocks and tested them with
cross-validation and against a global database of `r ram_stocks_n` stock
assessments. Ensemble methods substantially improved estimates of population
status and trend. Random forest and boosted regression trees performed the best
at estimating population status: accuracy improved `r
mean_sim$mach_vs_ind_mare_fold`%, rank-order correlation between predicted and
true status improved from `r mean_sim$ind_corr_range` to `r
mean_sim$mach_corr_range`, and bias (median proportional error) declined from
`r mean_sim$ind_mre_range` to `r mean_sim$mach_mre_range`.
We found similar improvements when predicting trend and when applying the
simulation-trained superensembles to catch data for global fish stocks.
Superensembles can optimally leverage multiple model predictions;
however, they must be tested, formed from a diverse set of accurate models, and
built on a dataset representative of the populations to which they are applied.

@@

Status and trend are two of the most fundamental values to quantify in the
management of ecological populations [e.g., @hutchings2010; @iucn2015]. However,
managers are often faced with reconciling multiple uncertain and potentially
conflicting estimates of status and trend [e.g., @brodziak2010; @branch2011;
@deroba2015]. For example, one model may suggest a population is at risk and
declining in abundance while others may suggest it is not at risk and stable.

One solution is to take the average or weighted average of several model
predictions, i.e., an ensemble. Such ensembles are typically more accurate and
less biased than individual model estimates and can incorporate various types of  uncertainty, such as uncertainty in
model structure, initial conditions, and parameter estimation
[@dietterich2000; @araujo2007]. Ensembles are superior to individual models
in at least three ways: (1) statistically by averaging across models and
therefore being less likely to pick the "wrong" model, (2) computationally by
reducing the risk of getting stuck in a local optima, and (3)
representationally by expanding the range of hypotheses explored
[@dietterich2000]. This approach forms the basis of many machine learning
methods [e.g., @dietterich2000], has helped reconcile climate forecasts from
dozens of models [e.g., @murphy2004; @tebaldi2007; @ipcc2013], and even
improved early warning signs of malaria outbreaks [@thomson2006]. In ecology,
ensemble methods are sometimes used to improve species distribution modelling
[e.g., @araujo2007; @breiner2015] and indeed have been used to combine
estimates of population status and trend [e.g., @brodziak2010].

@@

We can exploit these characteristics by using the predictions from a group of
models as inputs into a separate statistical model. This technique, sometimes
called superensemble modelling [@krishnamurti1999], is common in climate and
weather forecasting [e.g., @yun2005; @mote2015]. The superensemble is fit to a
training dataset where outcomes are well known and then used to predict on a
dataset of interest. For example, @krishnamurti1999
combined predictions of wind and precipitation in Asian monsoons via a
superensemble regression fit to observed data. Their superensemble was
considerably more accurate than any individual prediction or weighted average
of predictions.

In fisheries science, the commonly used operational models for determining
status and trend of exploited fish populations are stock assessments, i.e.,
population models coupled to an observation model that incorporate all
appropriate data (e.g., catches, size and age distributions, surveys, and
tagging information) to quantify values such as the biomass of a stock that
can produce maximum sustainable yield ($B_\mathrm{MSY}$) [@hilborn1992].
However, the broad range of data required to conduct these stock assessments
are not available for the majority of fish populations, including those of
conservation concern and of economic interest to fisheries [@fao2014].
Therefore, a number of models have been proposed to assess $B/B_\mathrm{MSY}$
based on the limited data available for the majority of fish stocks: (1) a time
series of the total weight of catch and (2) a basic understanding of
population productivity [e.g., @vasconcellos2005; @martell2013]. Recently,
@rosenberg2014 investigated the performance of four data-limited models through
a large-scale simulation experiment. Three of these models were based on
Schaefer (logistic) biomass dynamics and one was an empirical model fitted to
more data-rich stock-assessment output. The four models frequently disagreed
about population status (e.g., Fig. \ref{motivate}), no one model had strong
performance across all fish stocks, and some models performed better than
others depending on circumstances.

@@

To test the ability of superensembles to improve estimates of status and trend
in data-limited fish stocks, we first fit four individual assessment models to a
large simulated dataset of fish stocks. We then built and tested the performance
of superensembles using cross-validation of the simulated dataset. Finally, we
tested superensembles built with the entire simulated dataset against a database
of global fish stocks. We describe these steps in detail below and illustrate
the general approach both with illustrations and pseudocode in Fig. 2.

@@

* *CMSY* (catch-MSY) implements a stock-reduction analysis with Schaefer
  biomass dynamics [@martell2013]. It requires a prior distributions on $r$ and $K$
  as well as priors on the relative proportion of biomass at the beginning and end of the time
  series compared to unfished biomass (depletion). The version of
  the model used in @rosenberg2014 was modified from @martell2013 to generate
  biomass trends from all viable $r$-$K$ pairs and produce an estimate of
  $B/B_\mathrm{MSY}$ from the median trend.

@@

We first developed and tested ensemble methods on a fully factorial simulated
dataset of fisheries [@rosenberg2014] with known status. These simulated data
included the following scenarios: three fish life histories: small pelagic,
demersal, and large pelagic; three levels of initial biomass depletion
compared to carrying capacity: biomass at 100%, 70%, and 40% of carrying
capacity; and four exploitation settings: (1) a constant exploitation rate,
(2) an exploitation rate coupled with biomass to mimic an open-access
single-species fishery, (3) a scenario where exploitation rate increased
continuously, and (4) a "roller-coaster" scenario where the exploitation
rate increased and then decreased. Process noise (recruitment variability;
i.e., unexplained variability in population dynamics) was introduced to the
models at two magnitudes in log space, $N(0, 0.2^2)$ and $N(0, 0.6^2)$,
and was either uncorrelated through time or had first-order autoregressive
correlation of $0.6$. The simulation also included a scenario with $N(0,
0.2^2)$ measurement error around log(catch) and one scenario without
measurement error. @rosenberg2014 ran ten iterations for each combination
of factors adding stochastic draws of recruitment and catch-recording
variability each time to generate a total of 5760 stocks. The simulation
models were built in the `FLR` packages [@kell2007,
<http://flr-project.org>] for the statistical software R. Code to
generate the simulations is available at
<https://github.com/iagomosqueira/stockStatusFAO>.

@@

The individual models we seek to combine with superensembles provide time series
of stock status ($B/B_\mathrm{MSY}$). Therefore, we can use superensembles to
estimate any property of these time series. Here, we focus on two properties:
the mean and slope of $B/B_\mathrm{MSY}$ in the last five years. Together, these
quantities address the recent state and trend of stock status, which are both of
management and conservation interest [e.g., @hutchings2010; @iucn2015]. To avoid
undue influence of the time series end points on the calculated slope, we
measured the slope as the Theil-Sen estimator of median slope [@theil1950].

@@

@@

Once the superensemble models are built and trained using the simulated stocks
(or any dataset with "known" status), we can use the superensembles to estimate
the status of new stocks (Fig. \ref{didactic}b). To do this we applied the
individual models to our stocks of interest (i.e., CMSY, COM-SIR, SSCOM, mPRM)
and then used these individual model estimates of status or trend as data in our
already built superensemble models. In this paper we applied the superensemble
models to subsets of the simulated data as a cross-validation test to test
predictive performance and to the RAM Legacy Stock Assessment database to test
predictive performance on real stocks.

We used repeated three-fold cross validation: we randomly divided the dataset
into three sets, built superensemble models on two-thirds of the data, and
evaluated predictive performance on the remaining third. We repeated this across
each of the three splits and then repeated the whole procedure 50 times to
account for bias that may result from any one set of validation splits. In the
simulated dataset, there were 10 replicates of each unique combination of
simulation parameters that differed only in stochastic variability. Since the
dynamics of these populations were often similar, we grouped these stocks in the
cross-validation process into either the training or testing split.

@@

Predictive performance can be evaluated with metrics that represent a variety
of modelling goals. For continuous response variables such as the mean and
slope of population status, performance metrics often measure some form of
bias, precision, accuracy (a combination of bias and precision), or the ability
to correctly rank or correlate across populations [e.g., @walther2005]. Here, we
measure proportional error, defined as $(\hat{\theta} - \theta)/\abs{\theta}$,
where $\hat{\theta}$ and $\theta$ represent estimated and "true" (or
stock-assessed) mean or slope of $B/B_\mathrm{MSY}$. We calculated median
proportional error to measure bias, median absolute proportional error to
measure accuracy, and Spearman's rank-order correlation between predicted and
"true" values to measure the ability to correctly rank populations. When
testing with the RAM Legacy Stock Assessment database, we treated the
estimates from these data-rich stock assessments as known without error. Thus,
any error in the stock-assessment estimates of the mean or slope of
$B/B_\mathrm{MSY}$ also contributes to our estimates of prediction error for
each of the four data-limited models and the ensembles. Code to reproduce our
analysis is available at <https://github.com/datalimited/ensembles> (*Private while in
review*).

@@

Applied to the simulated dataset of known stock status, the individual models
had variable success at estimating the mean (status) and slope (trend) of
$B/B_\mathrm{MSY}$ in the last five years. All models exhibited a high degree of
scatter around the one-to-one line of perfect status prediction (Fig.
\ref{hexagon}). In contrast to the known unimodal distribution of status, CMSY
exhibited bimodal predictions (Fig. \ref{hexagon}a), but had the best rank-order
correlation and accuracy scores (Fig. \ref{performance}a). COM-SIR and SSCOM
both correctly identified a number of stocks with low status, but frequently
predicted a high status when status was in fact low (Fig. \ref{hexagon}b, c).
mPRM had relatively poor ability to predict status for the simulated dataset
(Fig. \ref{hexagon}d). There was generally little correlation between true and
predicted recent trend in status for any of the individual models (rank-order
correlation = `r range_slope_corr_non_sscom`) with the exception of SSCOM
(correlation = `r slope_corr_sscom`; Figs \ref{scatter-sim-slope}a--d).

@@

Ensemble methods provide a useful approach to situations where environmental
resource management decisions must be made on the basis of multiple,
potentially contrasting estimates of status. Compared to individual models of
fish population status, ensemble methods were consistently the best or among
the best across three performance dimensions (accuracy, bias, and rank-order
correlation), two response variables (status and trend), two datasets
(simulated and global fisheries), and multiple ensemble methods (from a simple
average to machine learning superensembles). Our results suggest choosing a
superensemble model that allows for non-linear relationships, such as
machine learning methods; these models provided added insight into individual
model behavior and generally performed the best.

Certain conditions will make some ensemble models more effective than others.
First, ensembles will be most effective when they are comprised of diverse
individual models that choose different structural model forms, explore
contrasting but plausible ranges of parameter values, and make uncorrelated
errors [@ali1996; @dietterich2000; @tebaldi2007]. We would expect such models
to perform well in different conditions and an ensemble model can
exploit the best predictive performance of each. Second,
ensemble models will be most effective when they are not overfit to the
training dataset. Cross-validation testing [@caruana2004; @hastie2009] and
methods that are robust to overfitting such as random forests [@breiman2001],
may help avoid overfitting ensemble models. We note that our simplest ensemble
model, an average of individual model predictions, performed approximately as
well as complex machine learning models when we trained our superensembles on
the simulation dataset and tested them on a separate "real" dataset (i.e., the
RAM Legacy Stock Assessment database, Fig. \ref{performance}b). Third, ensemble
models will be most effective when they are trained on data that are
representative of the dataset of interest [@knutti2009; @weigel2010].
Cross-validation within a training dataset will provide an optimistically
biased impression of predictive performance if the training dataset
fundamentally differs from the dataset of interest [@hastie2009].

Multi-model inference in the form of coefficient averaging weighted by
information theoretics such as the Akaike Information Criterion (AIC) is
a common analytical approach in fisheries and ecology [e.g., @burnham2002; @johnson2004;
@grueber2011]. The ensemble methods described in this paper share similarities
with coefficient averaging but differ in other important ways. Ensemble methods
and coefficient averaging share the long-held notion that multiple working
hypotheses can contribute useful information for inference [@chamberlin1890].
A fundamental difference is that coefficient averaging focuses on averaging
*coefficients* whereas ensembles instead average *predictions*. Thus, ensembles
provide a general purpose tool: they do not require information theoretics
and they can combine different types of models (e.g., parametric and
non-parametric models or frequentist and Bayesian predictions). Furthermore,
superensembles extend these benefits by allowing model predictions to be
combined via non-linear functions that are tuned to known data.

A strength of superensembles is that they can be tailored to predict specific
response variables. For example, we built separate superensemble models of mean
$B/B_\mathrm{MSY}$ and the slope of $B/B_\mathrm{MSY}$. The same set of model
weights or non-linear relationships need not hold across different response
variables. For instance, SSCOM contributed little to the GBM superensemble
estimate of status at higher levels of predicted $B/B_\mathrm{MSY}$ (Fig.
\ref{partial-sim}), but contributed strongly to estimates of trend (Fig.
\ref{partial-sim-slope}). Formally, fitting superensemble models to specific
quantities of interest (such as the slope of $B/B_\mathrm{MSY}$) provides an additional
calibration step [@rykiel1996]. Individual models are typically calibrated
(i.e., parameters are estimated) based on a single response variable; however,
this model might then provide a biased or inaccurate estimate of other
quantities of interest. Ensemble methods provide a final calibration step to a
quantity of interest. This ensemble calibration could include a loss function
tailored to the goals of the model, say placing greater weight on accuracy at
lower rather than higher status levels. Conversely, because superensembles are
tailored to a specific response and loss function, superensembles force a
modeller to choose an operational purpose for their model up front [*sensu*
@dickey-collas2014].

@@

Combining predictions from multiple models via superensemble methods is
broadly useful in other subfields of fisheries science and ecology in general.
Predictions about extinction risk are widely used at the national (e.g., the US Endangered
Species Act and the Canadian Species at Risk Act) and international [e.g., the
IUCN Red List, @iucn2015] levels. These risk assessments generally involve
fitting regression models to outcomes for individual species along with
predictors of extinction risk [e.g., @anderson2011a; @pinsky2011], or fitting population-dynamic models to data for individual species [e.g., @dfo2010]. Both types of
models are prone to error caused by model-misspecification and therefore results
are sensitive to decisions about model structure [@brooks2015]. Although there
are options to account for potential model-misspecification in determination of
species risk [e.g., coefficient averaging, @burnham2002; generalized modeling,
@yeakel2011; or semi-parametric methods, @thorson2014], ensemble methods are
a relatively simple way to combine predictions in a transparent manner. Beyond
estimates of status and trend, ensemble methods could be used, for example, to
increase the robustness of spatial predictions when designing networks of
protected areas [@rassweiler2014] or to forecast potential spatial shifts in
species distribution given climate impacts [@harsch2014].
